\chapter*{杰克与露西 / Jack and Lucy}
\addcontentsline{toc}{chapter}{杰克与露西 / Jack and Lucy}

\section*{从前有一个村庄 / Once Upon a Time, There Was a Village}

在一个安静的小村庄里，住着一对年轻的夫妻，杰克和露西。露西是一位非常优秀的英语老师，她勤奋敬业，深受学生们的喜爱。然而，尽管她工作上取得了很大的成功，她总是感到有些疲惫。繁重的工作和课堂上的压力让她感到力不从心。尽管她努力平衡工作和生活，但有时她依然感到无法应对的压力。

\begin{flushright}
In a quiet little village, there lived a young couple, Jack and Lucy. Lucy was an excellent English teacher, known for her diligence and the respect she earned from her students. However, despite her success, she often felt tired. The heavy workload, classroom pressures, and the expectations placed on her left her feeling drained. Though she worked hard to balance her work and personal life, at times, the fatigue seemed overwhelming.
\end{flushright}

杰克看着心爱的妻子日复一日地困扰，他决定要做些什么，帮助露西走出困境，重新找回她的活力和快乐。

\begin{flushright}
Jack, seeing his beloved wife struggling day after day, decided to do something to help Lucy overcome her weariness and bring back her vitality and joy.
\end{flushright}

\section*{杰克的决定 / Jack's Decision}

杰克想到了一个办法——他决定养一只鸡。他听说鸡的血做出来的美食能带来好运，而在这小小的村庄里，许多事情都与好运和好心情息息相关。杰克心想，或许一只鸡能给露西带来一些快乐和希望。

\begin{flushright}
Jack came up with an idea—he decided to raise a chicken. He had heard that the blood of a chicken, when used in cooking, could bring good fortune, and in this small village, good fortune and positive emotions were tightly intertwined. Jack thought that perhaps a chicken could bring some joy and hope to Lucy.
\end{flushright}

于是，他悄悄地去村里买了一只活泼的小母鸡，并把它带回家。露西并没有注意到这只鸡的存在，因为杰克每次都会把它藏好，只有他一个人照顾它。

\begin{flushright}
So, he quietly went to the village and bought a lively little hen, then brought it back home without Lucy noticing. Jack kept the chicken hidden, caring for it alone.
\end{flushright}

\section*{秘密的夜晚 / The Secret Nights}

每当夜深人静，露西沉沉入睡时，杰克便会起床。他不是去工作，而是去照顾那只鸡。他从鸡身上取一些血，用来做菜。他知道，这些美食不仅能带来身体上的温暖，还能让露西的心情放松和治愈。

\begin{flushright}
Every night, when Lucy was fast asleep, Jack would wake up. He didn’t go to work; instead, he would take care of the chicken. He would carefully take some of the chicken's blood and use it to cook dishes with fresh vegetables. For example, he would make braised chicken with seasonal vegetables, where the chicken blood would blend in gently during the cooking process, giving the dish a warming and soothing effect. Although Lucy never noticed any oddity in the taste, every time she ate the food, she felt an inner peace and ease.
\end{flushright}

然而，杰克并没有告诉露西这些事情。他不想让她担心，他只是默默地为她做这些。每当他做这些菜品时，他心里都会默默祈祷，希望这些食物能帮助露西恢复她的活力和快乐。

\begin{flushright}
Jack never told Lucy about these efforts. He didn’t want her to worry. He simply wanted to do it quietly for her. Every time he made these meals, using chicken blood with vegetables, he silently hoped that it would bring her happiness and ease her stress.
\end{flushright}

\section*{每日的惊喜 / The Daily Surprises}

除了照顾鸡，杰克还决定每天为露西做不同的饭菜。他会精心挑选新鲜的食材，制作美味的菜肴，让露西感受到家的温暖和他深深的爱。每顿饭后，杰克总会看着露西脸上的微笑，尽管她有时并不说话，但那种由衷的快乐让他知道，他的努力没有白费。

\begin{flushright}
In addition to caring for the chicken, Jack decided to cook a different meal for Lucy every day. He carefully selected fresh ingredients and made delicious dishes, making Lucy feel the warmth of home and his deep love. After every meal, Jack would watch her face light up with a smile. Even though she didn’t always say anything, the joy on her face assured him that his efforts were not in vain.
\end{flushright}

杰克还会在每天的饭后，悄悄放一些新鲜的花在桌上，或者送给露西一块小巧的巧克力。小小的细节，渐渐地开始改变露西的情绪。她发现自己变得更加开心、轻松，压力似乎减轻了许多。

\begin{flushright}
Jack would also secretly place fresh flowers on the table or give Lucy a small piece of chocolate after every meal. These small gestures gradually started to change Lucy's mood. She began to notice that she was becoming happier, lighter, and her stress seemed to melt away.
\end{flushright}

\section*{露西的觉醒 / Lucy’s Awakening}

有一天，露西突然意识到，自己最近的心情变得很好，压力也不再那么沉重。她开始想，究竟发生了什么变化。她细心地回想了一下，唯一不同的就是杰克每天都为她做饭，而且那些饭菜总是那么新鲜、美味。

\begin{flushright}
One day, Lucy suddenly realized that her mood had improved and her stress was no longer so overwhelming. She started wondering what had changed. After reflecting carefully, she realized that the only difference was that Jack had been preparing different meals for her every day, and they were always fresh and delicious.
\end{flushright}

她忍不住问杰克：“亲爱的，为什么你每天都做这些不同的饭菜给我吃？你是不是有什么秘密？”

\begin{flushright}
She couldn't help but ask Jack, "My dear, why do you make such different meals for me every day? Do you have some sort of secret?"
\end{flushright}

杰克笑了笑，眼里满是温柔：“没有什么秘密，只是我希望你每天都能开心，忘掉那些压力，感受到我的爱。”

\begin{flushright}
Jack smiled gently, his eyes full of tenderness, "There’s no secret, I just want you to be happy every day, to forget about the pressure, and to feel my love."
\end{flushright}

露西愣住了，心中充满了感动。她没有意识到，自己是如此幸运，能够拥有一个如此细心和体贴的丈夫。

\begin{flushright}
Lucy was taken aback, her heart filled with gratitude. She had never realized how lucky she was to have such a thoughtful and caring husband.
\end{flushright}

\section*{最后的秘密 / The Final Secret}

尽管露西日渐开心和自信，但她并不知道杰克所做的所有努力。她并不知道，那只鸡、鸡血、以及杰克那些悄悄的夜晚，都是为了她而做的。

\begin{flushright}
Although Lucy was becoming happier and more confident, she never knew all the efforts Jack had made. She didn't know that the chicken, the chicken blood, and the quiet nights Jack spent preparing meals were all for her.
\end{flushright}

杰克虽然从不向露西透露这些秘密，但他知道，自己所做的一切都值得。当他看到露西恢复了自信，重新笑颜常开时，他的内心充满了满足和喜悦。

\begin{flushright}
Jack never revealed these secrets to Lucy, but he knew that everything he had done was worth it. Every time he saw Lucy regain her confidence and smile, his heart was filled with satisfaction and joy.
\end{flushright}

\section*{结局 / The Ending}

最终，露西恢复了信心，她变得更加乐观和积极。她感谢丈夫杰克的关爱，虽然她并不知道背后的秘密。杰克的无私和耐心，让这段婚姻更加深厚和美好。

\begin{flushright}
In the end, Lucy regained her confidence and became more optimistic and positive. She thanked her husband Jack for his love, though she never knew the full story behind it. Jack's selflessness and patience made their marriage even stronger and more beautiful.
\end{flushright}

村里的人们也注意到露西变得更加开朗，他们都说，杰克是个有魔法的男人，他的爱和细心能改变一切。露西知道，杰克所做的一切，都是为了她，而她的快乐与信心，正是他最大的心愿。

\begin{flushright}
The people in the village also noticed that Lucy had become much more cheerful, and they all said that Jack was a man with magic, whose love and thoughtfulness could change everything. Lucy knew that everything Jack did was for her, and her happiness and confidence were his greatest wish.
\end{flushright}
