\chapter*{圣母与女巫的交易 / The Bargain Between the Virgin and the Witch}
\addcontentsline{toc}{chapter}{圣母与女巫的交易 / The Bargain Between the Virgin and the Witch}

在遥远的森林边缘，住着一位圣洁的女子。她的眼睛倒映着天光，她的耳朵倾听着万物。她的鼻息沾染着花露，她的唇间流淌着温暖的言语。人们称她为圣母，因为她的心比黄金更纯净，她的灵魂比泉水更清澈。  
\begin{flushright}
In the distant edge of the forest, there lived a pure woman. Her eyes reflected the daylight, her ears listened to all things. Her breath was scented with flowers, and her lips spoke warm words. People called her the Virgin, for her heart was purer than gold, and her soul clearer than spring water.
\end{flushright}

可是在森林深处，有一位黑暗中的窥伺者——女巫。她的心如石头般冰冷，她的舌尖缠绕着谎言。她嫉妒圣母的美好，她渴望拥有她的一切。  
\begin{flushright}
But in the depths of the forest, there was a watcher in the darkness—a witch. Her heart was as cold as stone, and her tongue wove lies. She envied the Virgin's beauty and longed to possess all that she had.
\end{flushright}

\section*{夜色中的请求 / The Request in the Night}

一天，月光如水，夜风微凉。  
一位衣衫褴褛的老妇拄着枯木拐杖，颤抖着叩响圣母的门。  
\begin{flushright}
One day, the moonlight was like water, and the night wind was cool.  
A ragged old woman, leaning on a dry wooden staff, trembled as she knocked on the Virgin's door.
\end{flushright}

“可怜的姑娘啊，”她的声音如枯叶飘落，“我的双眼已经瞎了，看不见这世界的色彩。求求你，给我一点光明，让我也能看见花朵的颜色。”  
圣母垂下睫毛，眼里满是怜悯。  
她轻轻摘下眼睛，放入老妇人的掌心。  
\begin{flushright}
“Poor child,” her voice fell like dry leaves, “My eyes have gone blind, I cannot see the colors of this world. Please, grant me a little light, so I too can see the flowers' colors.”  
The Virgin lowered her lashes, her eyes filled with pity.  
She gently plucked her eyes and placed it into the old woman's palm.
\end{flushright}

老妇人的嘴角微微上扬，她低低地笑了一声，消失在夜色之中。  
\begin{flushright}
The old woman's lips curled up slightly, and she chuckled softly, disappearing into the night.
\end{flushright}

\section*{微风中的叹息 / The Sigh in the Breeze}

日影渐斜，空气中浮动着花香与尘埃。  
老妇第二次来到圣母的屋前，双手紧紧掩住鼻子，声音哀戚。  
\begin{flushright}
The shadows of the day grew long, and the air was filled with the scent of flowers and dust.  
The old woman came for the second time to the Virgin's door, her hands tightly covering her nose, her voice sorrowful.
\end{flushright}

“可怜的姑娘啊，我的鼻子坏了，闻不到世间的芬芳，只有腐朽与霉烂相伴。求求你，让我也能感受到春天的味道。”  
圣母轻轻呼出一口气，取下自己的鼻子，放入老妇人的掌心。  
\begin{flushright}
“Poor girl,” she sighed, “My nose is broken, and I cannot smell the world's fragrance, only decay and rot accompany me. Please, grant me the scent of spring.”  
The Virgin softly exhaled, plucking her own nose and placing it into the old woman's palm.
\end{flushright}

老妇深深地嗅了一口气，露出了一丝满足的笑容，而圣母的世界，已无声、无光、无香。  
\begin{flushright}
The old woman took a deep breath, a satisfied smile crossing her face, while the Virgin's world was left silent, without light, without fragrance.
\end{flushright}

\section*{沉默中的交换 / The Exchange in Silence}

夜色再次笼罩大地，星光冷淡。  
老妇轻轻叹息，第三次来到了圣母的屋前。  
\begin{flushright}
Nightfall again enveloped the land, and the starlight was cold.  
The old woman sighed softly, arriving for the third time at the Virgin's door.
\end{flushright}

“善良的姑娘，我的嘴巴已经干枯，不能再说话，也不能唱歌。求求你，给我你的声音吧。”  
圣母这一次沉默了。  
她知道，这个老妇人不过是女巫的伪装，知道她的哀求不过是谎言。  
\begin{flushright}
“Kind girl, my mouth has withered, and I can no longer speak or sing. Please, give me your voice.”  
This time, the Virgin remained silent.  
She knew that the old woman was but a disguise of the witch, and that her pleas were nothing but lies.
\end{flushright}

可她依然微笑着，将嘴唇摘下，放在她的掌心。  
女巫终于不再伪装，她仰天长笑，声音如裂帛般刺耳。  
她挺直身子，恢复了真正的模样——一位邪恶而狡诈的女巫。  
\begin{flushright}
But she still smiled, plucking her lips and placing them into the woman's hand.  
The witch finally stopped disguising herself. She threw her head back and laughed long, her voice sharp as torn fabric.  
She straightened her back, revealing her true form—a wicked and cunning witch.
\end{flushright}

\section*{风声中的诉说 / The Plea in the Wind}

晨曦初露，树林间流淌着鸟鸣。  
那老妇又来了，她捂着耳朵，泪水滑落脸颊。  
\begin{flushright}
The morning light broke through, and the forest was filled with the songs of birds.  
The old woman came again, covering her ears, tears streaming down her cheeks.
\end{flushright}

“仁慈的姑娘，我什么也听不见，世界对我来说是无声的牢笼。求求你，让我也能听到风的歌唱。”  
圣母仍然微微一笑，轻轻割下耳朵，交到老妇人手里。  
\begin{flushright}
“Kind girl, I can hear nothing, the world is a silent prison to me. Please, let me hear the song of the wind.”  
The Virgin also smiled slightly, gently cutting off her ears and placing it into the old woman's hand.
\end{flushright}

老妇接过它，低声道了一句什么，可这一次，圣母没有听见。  
\begin{flushright}
The old woman took it and muttered something, but this time, the Virgin did not hear.
\end{flushright}

她睁开明亮的眼睛，看见世界；   
她深深吸气，闻到芬芳；  
她张开嘴唇，说出甜美的言语；
她竖起敏锐的耳朵，听见人声。 
\begin{flushright}
She opened her bright eyes and saw the world;  
She raised her sharp ears and heard the voices of people;  
She inhaled deeply, smelling the fragrance;  
She parted her lips and spoke sweet words.
\end{flushright}

而圣母呢？她失去了所有，成为沉默的黑暗。  
\begin{flushright}
And the Virgin? She lost everything, becoming silent darkness.
\end{flushright}

\section*{星辰无言，夜色依旧 / The Silent Stars, the Unchanging Night}

女巫带着圣母的一切，踏入人群。  
她用圣母的声音安慰世人，她用圣母的眼睛凝视温暖，她用圣母的耳朵聆听祈祷。  
\begin{flushright}
The witch, taking all that belonged to the Virgin, entered the crowd.  
She used the Virgin's voice to comfort the people, her eyes to gaze warmly, her ears to listen to prayers.
\end{flushright}

人们相信她是圣母，向她献上花束，向她低声祷告，向她诉说心事。  
而真正的圣母呢？  
她独自坐在森林的尽头，没有眼睛去看，没有耳朵去听，没有鼻子去闻，也没有嘴巴去诉说。  
\begin{flushright}
The people believed she was the Virgin, offering her flowers, whispering prayers, and confiding in her.  
But the true Virgin?  
She sat alone at the edge of the forest, with no eyes to see, no ears to hear, no nose to smell, and no lips to speak.
\end{flushright}

可她依然微笑着。  
\begin{flushright}
But she still smiled.
\end{flushright}

后来，人们渐渐遗忘了她，遗忘了真正的温柔与善良，遗忘了她的牺牲与给予。  
\begin{flushright}
Over time, people gradually forgot her, forgetting the true kindness and gentleness, forgetting her sacrifice and giving.
\end{flushright}

有人说，她并没有真正消失，而是化作了夜空中最明亮的星辰，静静地注视着这个世界。  
可世界，已听不到她的声音了。  
\begin{flushright}
Some say she did not truly disappear but became the brightest star in the night sky, silently watching over the world.  
But the world could no longer hear her voice.
\end{flushright}
